Using Fundamental Measure Theory to treat the Pair Distribution Function of the Inhomogeneous Hard-Sphere Fluid

### 2013-08-22 papers/pair-correlation/paper.tex
debugged sphere-with-wall.cpp and triplet-dft.cpp and modified some equations in paper Tested everything on node22.
Added 2d plot data for the path plots. Changed the names of the path plot scripts, they are now:    plot-path.py    plot-path-triplet-contact.py    plot-path-triplet-inbetween.py Also changed the name of their outputs, and adjusted the paper to use the new ones. Tested everything on paho-deb.

We construct $g(r, g_\sigma)$ using several constraints.  Naturally,
\begin{equation}
  g(\sigma, g_\sigma) = g_\sigma.
\end{equation}
In addition, we know that
\begin{equation}
  \begin{split}
  \int (g(r)-1)d\rr &= \frac{\chi_T}{kT} \\
  &= \eta \eta \cdots \fixme{fill in, double-check}
  \end{split}
\end{equation}
where $\chi_T$ is the isothermal compressibility, for which we use the
Carnahan-Starling equation of state.

@@

\begin{figure}
  \includegraphics[width=\columnwidth]{figs/pair-correlation-pretty-alt-1.pdf}
  \caption{Pretty plot of the pair distribution function near a hard
    wall.}\label{fig:pair-distribution-1}
\end{figure}

\begin{figure}
  \includegraphics[width=\columnwidth]{figs/pair-correlation-pretty-alt-2.pdf}
  \caption{Pretty plot of the pair distribution function near a hard
    wall.}\label{fig:pair-distribution-2}
\end{figure}
\begin{figure}
  \includegraphics[width=\columnwidth]{figs/pair-correlation-pretty-alt-3.pdf}
  \caption{Pretty plot of the pair distribution function near a hard
    wall.}\label{fig:pair-distribution-3}
\end{figure}
\begin{figure}
  \includegraphics[width=\columnwidth]{figs/pair-correlation-pretty-alt-4.pdf}
  \caption{Pretty plot of the pair distribution function near a hard
    wall.}\label{fig:pair-distribution-4}
\end{figure}

@@

\begin{figure}
  \includegraphics[width=\columnwidth]{figs/triplet-correlation-alt-3.pdf}
  \caption{The triplet distribution function
    $g^{(3)}(\rr_1,\rr_2,\rr_3)$ plotted when $\rr_1$ and $\rr_2$ are
    in contact.}\label{fig:triplet-distribution-3}
\end{figure}
\begin{figure}
  \includegraphics[width=\columnwidth]{figs/triplet-correlation-alt-4.pdf}
  \caption{Pretty plot of the pair distribution function near a hard
    wall.}\label{fig:triplet-distribution-4}
\end{figure}

>>>>

We construct $g(r, g_\sigma)$ using several constraints.  Naturally,
\begin{equation}
  g(\sigma, g_\sigma) = g_\sigma.
\end{equation}
In addition, we know that
\begin{equation}
  \begin{split}
    1 + n\int\left[g(r)-1\right]d\rr = nkT\chi_T\\
    \chi_T  = -\frac{1}{V}\left(\frac{\partial V}{\partial p}\right)_T
    = - \left(V\left(\frac{\partial p}{\partial V}\right)_T\right)^{-1}\\
    p = \frac{1+\eta+\eta^2-\eta^3}{(1-\eta)^3}\Longrightarrow \left(\frac{\partial p}{\partial V}\right)_T = \frac{dp}{d\eta}\frac{d\eta}{dV}\\
    \eta = \frac{4\pi R^3N}{3V}\Longrightarrow \frac{d\eta}{dV} = -\frac{\eta}{V}\\
    \left(\frac{\partial p}{\partial V}\right)_T = -\frac{\eta}{V}\left[\frac{1 + 2\eta - 3\eta^2}{(1-\eta)^3} + 3\frac{1 + \eta + \eta^2 - \eta^3}{(1-\eta)^4}\right]\\
  %\int (g(r)-1)d\rr &= \frac{\chi_T}{kT} \\
  %&= \eta \eta \cdots \fixme{fill in, double-check}
  \end{split}
\end{equation}
where $\chi_T$ is the isothermal compressibility, for which we use the
Carnahan-Starling equation of state.

@@

\begin{figure}
  \includegraphics[width=\columnwidth]{figs/pair-correlation-pretty-1.pdf}
  \caption{Pretty plot of the pair distribution function near a hard
    wall.}\label{fig:pair-distribution-1}
\end{figure}

\begin{figure}
  \includegraphics[width=\columnwidth]{figs/pair-correlation-pretty-2.pdf}
  \caption{Pretty plot of the pair distribution function near a hard
    wall.}\label{fig:pair-distribution-2}
\end{figure}
\begin{figure}
  \includegraphics[width=\columnwidth]{figs/pair-correlation-pretty-3.pdf}
  \caption{Pretty plot of the pair distribution function near a hard
    wall.}\label{fig:pair-distribution-3}
\end{figure}
\begin{figure}
  \includegraphics[width=\columnwidth]{figs/pair-correlation-pretty-4.pdf}
  \caption{Pretty plot of the pair distribution function near a hard
    wall.}\label{fig:pair-distribution-4}
\end{figure}

@@

\begin{figure}
  \includegraphics[width=\columnwidth]{figs/triplet-correlation-pretty-contact-3.pdf}
  \caption{The triplet distribution function
    $g^{(3)}(\rr_1,\rr_2,\rr_3)$ plotted when $\rr_1$ and $\rr_2$ are
    in contact.}\label{fig:triplet-distribution-3}
\end{figure}
\begin{figure}
  \includegraphics[width=\columnwidth]{figs/triplet-correlation-pretty-contact-4.pdf}
  \caption{The triplet distribution function
    $g^{(3)}(\rr_1,\rr_2,\rr_3)$ plotted when $\rr_1$ and $\rr_2$ are
    in contact.}\label{fig:triplet-distribution-4}
\end{figure}

\begin{figure}
  \includegraphics[width=\columnwidth]{figs/triplet-correlation-pretty-inbetween-3.pdf}
  \caption{The triplet distribution function
    $g^{(3)}(\rr_1,\rr_2,\rr_3)$ plotted when $\rr_1$ and $\rr_2$ are
    separated by the diameter of one sphere.}\label{fig:triplet-distribution-3}
\end{figure}
\begin{figure}
  \includegraphics[width=\columnwidth]{figs/triplet-correlation-pretty-inbetween-4.pdf}
  \caption{The triplet distribution function
    $g^{(3)}(\rr_1,\rr_2,\rr_3)$ plotted when $\rr_1$ and $\rr_2$ are
    separated by the diameter of one sphere.}\label{fig:triplet-distribution-4}
\end{figure}
